---
title: "3.20 Mon dplyr"
output: html_document
date: "2023-03-20"
---
需要最后filter的笔记!!
3.20 Mon
dplyr:
filter()picks cases based on values\
select()pics variables based on names\
arrange()changes the order of the rows\
mutate()add new variables that are function of existing variables\
summarise()reduces multiple variables to a single

```{r}
tip<-read.csv("tips.csv")
head(tip)
```
Filter the records\
Read the tips as data.frame and filter records for size=3 and tip>4\
```{r}
tips<-as.data.frame(tip)
tips[tip$size==3 & tips$tip>4,]
```
Read the tips as data.table and filter for size=3 and tip>4
```{r}
library(data.table)
dt<-as.data.table(tips)
head(dt)
dt[size==3 & tip>4,]
```
Dyplyr\
```{r}

library(dplyr)
filter(tips,size==3,tip>4)
```
#Select the variables of interest\
#select(tips,sex,size,tip)\
select(tips,contains("i"))\
select(tips,starts_with("s"))\
select(tips,ends_with("s"))\
select(tips,matches("a"))\
\
#Arrange or order the data
arrange(tips,size)\
arrange(tips,desc(size))\   #descending order\
arrange(tips,totbill,tip)\
\
#mutate: create a new variable\
```{r}
x<-mutate(tips,tiprate=tip/totbill)
write.csv(x,file="tips1.csv")   #save the data file
dir()
```
The piping operators: %>%
```{r}
y<-tips %>%
  filter(size>5)%>%
  select(totbill,tip,sex,day,size)%>%
  arrange(tip)%>%
  mutate(tiprate=tip/totbill)
y
```
Group by and then summarize
```{r}
tips%>%
  group_by(day)%>%
  summarize(mean(tip))
```
Exercise: select the records for the variable time that does not/does contain the letter "i"
```{r}
table(tips$time)
filter(tips,time=="night")
```
NYCflights
```{r}
flight<-read.csv("nycflights14.csv")
flights<-as.data.frame(flight)
head(flights)
```
```{r}
head(filter(flights,origin=="JFK",dest=="BTV"))
```








