---
title: "3.22 Wed dplyr"
output: html_document
date: "2023-03-22"
---

```{r}
df1<-data.frame(Name=c("A","B","C","D","E"),
               Sex=c("Male","Female","Female","Male","Female"),
               Age=c(20,22,23,21,22))
df1
df2<-data.frame(Name=c("A","E","G"),
                Weight=c(150,140,176),
                GPA=c(3.8,3.9,4.0))
df2
```
Left_join, the left is the base\
```{r}
library("dplyr")
left_join(df1,df2,by=c("Name"="Name"))
left_join(df2,df1,by=c("Name"="Name"))
```
Right_join, the right is the base\
```{r}
right_join(df1,df2,by=c("Name"="Name"))
right_join(df2,df1,by=c("Name"="Name"))
```
Inner_joing\
order does not matter
```{r}
inner_join(df1,df2,by=c("Name"="Name"))
inner_join(df2,df1,by=c("Name"="Name"))
```
Full_join\
keep all rows and columns in both set\
```{r}
full_join(df1,df2,by=c("Name"="Name"))
full_join(df2,df1)
```
anti_join\
Anti joinkeeps rows and variables only from the left data frame without a match\
```{r}
anti_join(df1,df2,by=c("Name"="Name"))
anti_join(df2,df1)
```
semi_join\
semi join keeps rows and variales only from the left data frame\
Difference is the column
```{r}
semi_join(df1,df2)
semi_join(df2,df1)
```
\
\
Joining more than 2 or more columns\
**Tibble**\
```{r}
d1<-tibble(
  x1=letters[1:3],
  y1=LETTERS[1:3],
  a=rnorm(3))
d1
```
```{r}
d2<-tibble(
  x2=letters[3:5],
  y2=LETTERS[3:5],
  b=rnorm(3))
d2
```

```{r}
df<-left_join(d1,d2,by=c("x1"="x2","y1"="y2"))
inner_join(d1,d2,by=c("x1"="x2","y1"="y2"))
df
```
\
Remove the NA rows\
complete.cases()
```{r}
filter(df,b==NA)
df%>%filter(complete.cases(df))
```
```{r}
data<-data.frame(
  x=c(1:3,2,4),
  c=c("A","B",NA,"B","D"))
data
```
Remove the NA and duplicate from the dataframe\
duplicated():identify duplicate elements\
unique(): keep only unique elements\
distinct():remove the duplicate in a data table\
```{r}
data1<-data%>%filter(complete.cases(data))
duplicated(data1)
unique(data1)
distinct(data1)
```
Using pipe
```{r}
data%>%
  filter(complete.cases(data))%>%
  distinct()
```
slide page
```{r}
bind_rows(d1,d2)
bind_cols(d1,d2)
```




