---
title: "HW6"
output: html_document
date: "2023-04-16"
---

```{r}
flight<-read.csv("flights.csv")
head(flight)

length(flight$year)
length(flight$month)
length(flight$day)

new<-paste(flight$year,flight$month,flight$day,sep="-")

library(chron)
x<-flight$dep_time
head(x,10)
x1<-times(sprintf("%d:%02d:00",x%/%100,x%%100))
head(x1,10)
class(x1)
new1<-paste(new,x1)
flight$deptime<-new1
flight1<-subset(flight,select=c(year,month,day,deptime))
head(flight1)

```
We did not learn the method to transfer the numeric elements to hours-minutes-seconds. Also, I cannot understand the meaning of the three digits in the flight$dep_time since there is no explanation. I thought it is a typo and used time_hour. It is painful to try and comeback to use dep_time, and search online. \

```{r}
library(dplyr)
library(ggplot2)
library(lubridate)

flight1$date<-as.Date(new)
flight1$weekday<-weekdays(flight1$date)
head(flight1)

mon<-sum(flight1$weekday=="Monday")
tue<-sum(flight1$weekday=="Tuesday")
wed<-sum(flight1$weekday=="Wednesday")
thr<-sum(flight1$weekday=="Thursday")
fri<-sum(flight1$weekday=="Friday")
sat<-sum(flight1$weekday=="Saturday")
sun<-sum(flight1$weekday=="Sunday")
```


```{r}
day<-data.frame(weekday=c("Mon","Tue","Wed","Thr","Fri","Sat","Sun"),
                total=c(mon,tue,wed,thr,fri,sat,sun))
day
color<-c("salmon","palegreen","lightpink","plum","palegreen3","lightblue","grey")
  
ggplot(day,aes(x=factor(weekday,level=c("Mon","Tue","Wed","Thr","Fri","Sat","Sun")),y=total))+
  geom_bar(stat="identity",fill=color)+
  xlab("Weekday")+
  ylab("Total count for weekday in 2013")+
  ggtitle("The Flights in Weekday in 2013")+
  theme(axis.title.x=element_text(),
        axis.title.y=element_text(angle=0,vjust=0.5))

mean(day$total)
```
Findings: The bar plot shows that the departure flights in NYC are relatively low in weekends compared to weekdays. The mean depature flights is 48110 for each weekday. 
```{r}
#head(flight)
#flight2<-flight%>%
  #summarize(mean(dep_delay))%>%
  #group_by(hour)

```
I tried pipping here but it does not work.
```{r}
meandepature<-aggregate(data=flight,dep_delay~hour,FUN=mean)
head(meandepature)

ggplot(meandepature,aes(x=hour,y=dep_delay))+
  geom_line(color="blue")+
  theme(axis.title.y=element_text(angle=0))
```
```{r}
flight1$dep_delay<-flight$dep_delay
daydelay<-aggregate(data=flight1,dep_delay~weekday,FUN=mean)

ggplot(flight1,aes(x=weekday,y=dep_delay))+
  geom_bar(stat="identity",fill="salmon")
```
We should depart at Saturday as there is a minimum delay in the departure time based on the data from 2013 flights.\
\
**MFI**
Money flow index is the index that can show the trend when the price and the oscillator move to the opposite way.
```{r}
library(quantmod)
AMD<-loadSymbols("AMD",auto.assign=F,
                 from="2023-03-15",to="2023-04-16")
AMD30<-as.data.frame(AMD)
tail(AMD30)
```

```{r}
chartSeries(AMD30,
            type="bars",
            theme=chartTheme("white"))
```


